### 2013-11-09 article2013.Rmd
Now it works. Mikko text included and my corrections with the plots. Now using KOMA script and everything looks good!

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% October 2013

[^*]:*Work in progress

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --latex-engine=xelatex -o article2013.pdf")
system("~/.cabal/bin/pandoc article2013.md  --number-sections -o article2013.pdf")

@@

# jos multilevelit mukana
#system("~/.cabal/bin/pandoc article2013.md --number-sections --template=tex_templates/dcolumn.latex -o article2013.tex")
#system("perl -pi -e 's/footnotesize/tiny/g' article2013.tex")
#system("pdflatex article2013.tex")

@@

**Abstract**

*Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.*

@@

```{rarticleModels, results='asis', eval=TRUE}
load("data/finalModels.RData")

@@

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),float.pos="H",
       use.packages=TRUE,
       #booktabs=TRUE,
       #dcolumn=TRUE,
       #sideways=TRUE,
       naive = TRUE,
       caption.above=TRUE,
       doctype=FALSE,
       custom.model.names = model.names.multi.2,
       custom.coef.names = coef.names.multi,
       include.pvalues=TRUE,
       caption="Logistic multilevel random intercept model for social and individual blame type of explanation")

>>>>

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% November 2013

[^*]:*Work in progress. See the computation analysis at [research.muuankarski.org/attributions/](http://research.muuankarski.org/attributions/)

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=en -V papersize:a4paper -V documentclass=scrreprt -o article2013.pdf")
# Kuvat kohdalleen - avaa päätte
~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=en -V papersize:a4paper -V documentclass=scrreprt -o article2013.tex
sed -i 's/begin{figure}\[htbp\]/begin{figure}\[H\]/g' article2013.tex
xelatex article2013.tex

@@

@@

\begin{abstract}
Utilising The Life in Transition Survey (LiTS) conducted in 2010, the purpose of the paper is to examine public perceptions of the causes of poverty in Europe and Western Asia with special emphasis on post-socialist countries. The study applies multilevel techniques in order to analyse the role of individual and country-level explanatory factors as determinants of poverty attributions. As country-level determinants, paper analyses the changes in country's economic performance during the period of global financial crises, income inequality and the state of democracy. As individual-level determinants, the paper tests to what extent risk factors related to financial hardship are associated with perceptions of the causes of poverty.
\end{abstract}

@@

```{rarticleModelsSoc, results='asis', eval=TRUE}
load("data/finalModels.RData")

model.names.multi = c("Empty",
                      "Only individual",
                      "Gini added",
                      "GDP change added",
                      "Good governance added")

texreg(list(soc.0,
        soc.1,
        soc.2,
        soc.3,
        soc.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        include.pvalues=TRUE,
        caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

```{rarticleModelsInd, results='asis', eval=TRUE}
texreg(list(ind.0,
        ind.1,
        ind.2,
        ind.3,
        ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        use.packages=TRUE,
        include.pvalues=TRUE,
        #sideways=TRUE,
        scriptsize=TRUE,
        caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

```{rarticleModelsFull, results='asis', eval=TRUE}
load("data/finalModels.RData")

@@

library(texreg)
texreg(list(soc.4,ind.4,socVsInc),float.pos="H",
       use.packages=TRUE,
       #booktabs=TRUE,
       #dcolumn=TRUE,
       scriptsize=TRUE,
       naive = TRUE,
       caption.above=TRUE,
       doctype=FALSE,
       custom.model.names = model.names.multi.2,
       custom.coef.names = coef.names.multi,
       include.pvalues=TRUE,
       caption="Logistic multilevel random intercept model for social and individual blame type of explanation")

### 2013-11-09 finalPlots.Rmd
Now it works. Mikko text included and my corrections with the plots. Now using KOMA script and everything looks good!

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013")
#########################################
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2","#D55E00", "#CC79A7")

@@

```{rattribFinalPlotsGDP}
# valitaan vaan kohdemaat

t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)
plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

pdf("figure/scatter_gdp.pdf", width=14/2.54, height=22/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_gdp.png", width=14/2.54*ppi, height=22/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

pdf("figure/scatter_gini.pdf", width=14/2.54, height=22/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_gini.png", width=14/2.54*ppi, height=22/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

pdf("figure/scatter_wbgi.pdf", width=14/2.54, height=22/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_wbgi.png", width=14/2.54*ppi, height=22/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

@@

```{rattribFinalPlotsMap}
library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))

@@

map$group_analysis <- factor(map$group_analysis, levels=c("Western Europe",
                                                             "CEE",
                                                             "CIS",
                                                             NA))

@@

pdf("figure/mapplot.pdf", width=14/2.54, height=10/2.54)
mapplot
dev.off()

ppi <- 300
png("figure/mapplot.png", width=14/2.54*ppi, height=10/2.54*ppi, res=ppi)
mapplot
dev.off()

>>>>

```{rattribFinalPlotsLoad}
library(ggplot2)
library(gridExtra)
library(plyr)
library(grid)
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013")
#########################################
cbPalette <- c("#E69F00","#56B4E9","#999999","#009E73", "#F0E442", "#0072B2","#D55E00", "#CC79A7")

@@

```{rattribFinalPlotsGDP}
# valitaan vaan kohdemaat #
t3 <- subset(macro, group_fine != 'West Europe')
west <- subset(macro, group_fine == 'West Europe')
#t3 <- macro
#########################################
t3$group1 <- "group1"
func <- function(t3)
{
  return(data.frame(COR = cor(t3$socialBlame, t3$gdpchange07.10)))
}
df.cor <- ddply(t3, .(group1), func)
t4 <- join(t3,df.cor,by="group1")
cnames <- round(stats:::aggregate.formula(cbind(socialBlame, gdpchange07.10) ~ COR, data=t4, mean),2)

plot1 <- ggplot(t4, aes(x=gdpchange07.10, y=socialBlame, 
                        label=cntry)) +
  geom_smooth(method=lm, se=FALSE,  alpha=.5, linetype="dashed", size=0.5) +  
  geom_text(data=cnames, aes(gdpchange07.10,socialBlame, label = COR, group=COR), 
            size=2.5, color="black") +
  geom_text(size=2, vjust=-0.8, hjust=0.5) +
  geom_point(size=1.5) +
  geom_point(data=t4, aes(x=gdpchange07.10, 
                          y=socialBlame, color=group_general)) +
  # west reference
  geom_point(data=west, aes(x=gdpchange07.10, 
                          y=socialBlame, 
                            color=group_general), alpha=.5) +
  geom_text(data=west, aes(x=gdpchange07.10, 
                           y=socialBlame, label=cntry),
             alpha=.5, size=2, vjust=-0.8, hjust=0.5) +
  # west reference
  labs(x = "Change in GDP between 2007 and 2010 (%)", 
       y = "Support for social blame type of explanation (%)") + 
  scale_colour_manual(values=cbPalette) +
  coord_cartesian(xlim=c(-25,100)) +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  theme(legend.text=element_text(size=6)) +
  theme(legend.position="top") +
  theme(axis.title.y = element_text(size=6)) +
  theme(axis.title.x = element_text(size=6)) +
  theme(axis.text.y = element_text(size=6)) +
  theme(axis.text.x = element_text(size=6)) +
  #guides(color = guide_legend(nrow = 2)) +
  theme(legend.key.size = unit(3, "mm"))

@@

pdf("figure/scatter_gdp.pdf", width=12/2.54, height=18/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_gdp.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

pdf("figure/scatter_gini.pdf", width=12/2.54, height=18/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_gini.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()
```

@@

pdf("figure/scatter_wbgi.pdf", width=12/2.54, height=18/2.54)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

ppi <- 300
png("figure/scatter_wbgi.png", width=12/2.54*ppi, height=18/2.54*ppi, res=ppi)
grid.arrange(plot1,plot2, ncol=1)
dev.off()

@@

```{rattribFinalPlotsMap}

library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))

@@

@@

pdf("figure/mapplot.pdf", width=14/2.54, height=12/2.54)
mapplot
dev.off()

ppi <- 300
png("figure/mapplot.png", width=14/2.54*ppi, height=12/2.54*ppi, res=ppi)
mapplot
dev.off()

### 2013-11-09 index.Rmd
Now it works. Mikko text included and my corrections with the plots. Now using KOMA script and everything looks good!

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Regression modelling somewhat done for Turku seminar.

@@

# Paper

- [Article draft in .html](article2013.html)
- [Article draft in .pdf](article2013.pdf)
- [Article draft in .epub](article2013.epub)
- [Article draft in .docx](article2013.docx)

>>>>

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon
20131105  Regression modelling almost finished. Bug in a software caused a delay. Will be fixed by Wed morning. Now the tables are there, but coef and model names are not customized.
20131106  Regression modelling somewhat done for Turku seminar.
20131109  Corrections from Turku and the text restuctured. Methods needs to be opened

@@

# Article draft

-------------------
pdf-output                                                source code
------------                                              --------------
[Article draft in .pdf](article2013.pdf)                  [source](article2013.Rmd)
-------------------

### 2013-11-09 regressionModelling.Rmd
ennen kuin aloitan semman korjaukset
Regression tables added and pandoc works ok. Booktabs and dcolumn would be nice
Now it works. Mikko text included and my corrections with the plots. Now using KOMA script and everything looks good!

htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
          caption="Logistic multilevel random intercept model for social blame type of explanation", 
        caption.above=TRUE)

@@

>>>>

htmlreg(list(ind.0,
       ind.1,
       ind.2,
       ind.3,
       ind.4),
        custom.model.names = model.names.multi,
        custom.coef.names = coef.names.multi,
        naive = TRUE,
        ci.test = NULL,
        inline.css = FALSE,
        doctype = FALSE,
        html.tag = FALSE,
        head.tag = FALSE,
        body.tag = FALSE,
        include.pvalues=TRUE,
          caption="Logistic multilevel random intercept model for individual blame type of explanation", 
        caption.above=TRUE)

@@

save(ind.0,ind.1,ind.2,ind.3,ind.4,
     soc.0,soc.1,soc.2,soc.3,soc.4,
     socVsInc, file="data/finalModels.RData")
